A Methodology and Implementation of Automated Emissions Harmonization for Use in Integrated Assessment Models

### 2017-05-18 meth.tex
add method table

@@

\subsection{Implemented Methods}\label{sec:impl-meths}

>>>>

The \code{aneris} code base provides a family of methods to choose from for each
of the harmonization cases. A summary of all available methods is provided below
in Table \ref{tab:meths}.

\begin{table}[]
\centering
\caption{All Harmonization Methods Provided in \code{aneris}}
\label{my-label}
\begin{tabular}{|l|l|l|}
\hline
Method Name                             & Harmonization Type & Convergence Year\\
\hline
\code{constant\_ratio}                  & ratio              & $t_f = \infty$\\
\code{reduce\_ratio\_<year>}            & ratio              & $t_f = $\code{<year>}\\
\code{constant\_offset}                 & offset             & $t_f = \infty$\\
\code{reduce\_offset\_<year>}           & offset             & $t_f = $\code{<year>}\\
\code{linear\_interpolate\_<year>}      & interpolation      & $t_f = $\code{<year>}\\
\hline
\end{tabular}
\end{table}

@@
